%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Medium Length Graduate Curriculum Vitae
% LaTeX Template
% Version 1.1 (9/12/12)
%
% This template has been downloaded from:
% http://www.LaTeXTemplates.com
%
% Original author:
% Rensselaer Polytechnic Institute (http://www.rpi.edu/dept/arc/training/latex/resumes/)
%
% Important note:
% This template requires the res.cls file to be in the same directory as the
% .tex file. The res.cls file provides the resume style used for structuring the
% document.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

%----------------------------------------------------------------------------------------
%	PACKAGES AND OTHER DOCUMENT CONFIGURATIONS
%----------------------------------------------------------------------------------------

\documentclass[margin, 10pt]{res} % Use the res.cls style, the font size can be changed to 11pt or 12pt here

\usepackage{helvet} % Default font is the helvetica postscript font
%\usepackage{newcent} % To change the default font to the new century schoolbook postscript font uncomment this line and comment the one above
\usepackage{enumitem}
\usepackage{url}
\usepackage{biblatex}

\setlength{\textwidth}{5.1in} % Text width of the document

\begin{document}

%----------------------------------------------------------------------------------------
%	NAME AND ADDRESS SECTION
%----------------------------------------------------------------------------------------

\moveleft.5\hoffset\centerline{\large\bf Hayoung Chung, Ph.D.} % Your name at the top
 
\moveleft\hoffset\vbox{\hrule width\resumewidth height 1pt}\smallskip % Horizontal line after name; adjust line thickness by changing the '1pt'
 
 
\moveleft.5\hoffset\centerline{Postdoctoral Researcher}
\moveleft.5\hoffset\centerline{Department of Structural Engineering}
\moveleft.5\hoffset\centerline{University of California, San Diego}
\moveleft.5\hoffset\centerline{hac210@ucsd.edu; summeryoung88@gmail.com}

% \moveleft.5\hoffset\centerline{Rm. 442, SME Building} % Your address
% \moveleft.5\hoffset\centerline{Department of Structural Engineering}
% \moveleft.5\hoffset\centerline{University of California, San Diego}
% \moveleft.5\hoffset\centerline{hac210@ucsd.edu, summeryoun88@gmail.com}
% \moveleft.5\hoffset\centerline{(858) 284-6782}

%----------------------------------------------------------------------------------------

\begin{resume}

%----------------------------------------------------------------------------------------
%	OBJECTIVE SECTION
%----------------------------------------------------------------------------------------
 
\section{EXPERTISE}  
\begin{itemize}
    \item Computational mechanics of multifunctional structural materials 
    \item Development of numerical algorithms for structural design considering \\ multiphysics 
\end{itemize}
    
%----------------------------------------------------------------------------------------
%	EDUCATION
%----------------------------------------------------------------------------------------
\section{EDUCATION}

\textbf{Seoul National University (Korea) \hfill September 2010 - February 2017} \\
\textbf{Ph.D.} in \textit{School of Mechanical and Aerospace Engineering} \\ 
\textit{Thesis: A multiscale analysis and design of the light-responsive liquid crystal polymer using nonlinear finite element shell model} (Advisor: Prof. Maenghyo Cho)\\ 
\textit{GPA}: 3.84/4.30 \\

\textbf{Seoul National University (Korea) \hfill March 2006 - August 2010} \\
\textbf{B.S.} in \textit{School of Mechanical and Aerospace Engineering} \\
\textit{GPA}: 3.72/4.30; \textit{Cum Laude}, Within top 15\% \\

%----------------------------------------------------------------------------------------
%	EXPERIENCE SECTION
%----------------------------------------------------------------------------------------
\section{EXPERIENCE} 

\textbf{University of California, San Diego \hfill March 2017 - Present} \\
\textit{Postdoctoral Researcher} \\ 
\begin{enumerate}
    \item \textbf{OpenLSTO}, \textit{Open-source software for level-set topology optimization} 
    \\ https://github.com/M2DOLab/OpenLSTO
    \begin{itemize}
        \item One of the main developers of OpenLSTO
        \item Main Github repository maintainer
    \end{itemize}
    
    \item \textbf{Topology optimization using OpenMDAO (Sponsor: \textit{NASA})} \\
    https://github.com/chungh6y/openmdao\_TopOpt
    \begin{itemize}
        \item OpenMDAO is an open-source, Multidisciplinary Design Optimization framework. 
        \item Presented and implemented a modular interpretation of topology optimization algorithms
        \item Flexibility and easy reconfigurability of the algorithms are greatly enhanced
        \item Optimized the performance by using a C++ finite element code (\textit{Cython})
    \end{itemize}
    
    \item \textbf{Nonlinear thermoelastic level-set topology optimization (Sponsor: DARPA)}
    \begin{itemize}
        \item Developed the nonlinear thermoelastic finite element model
        \item Designed thermoelastic structures experiencing large deformations
        \item Executed a sensitivity analysis of large deforming structures
        \item Identified nonlinear effects on the structural design under a high-temperature thermal load
    \end{itemize}
\end{enumerate}

\textbf{Texas Super Computing Center \hfill October 2018} \\
\textit{Hackathon participant}

\begin{enumerate}
    \item Participated TRADES problem (DARPA) discussion
\end{enumerate}

\textbf{NASA Glenn Research Center \hfill August 2017} \\
\textit{Research Visitor}

\begin{enumerate}
    \item Invited to collaborate with the researchers and programmers in implementing level-set topology optimization within OpenMDAO
\end{enumerate}

\textbf{Seoul National University \hfill August 2010 - February 2017} \\
\textit{Graduate Research Assistant}

\begin{enumerate}
    \item \textbf{Multi-scale simulation for photo-polymerization (Sponsor: Samsung Display)}
    \begin{itemize}
        \item Developed a finite element method to study topological changes of liquid crystal alignments in the existence of an external field 
    \end{itemize}
    
    \item \textbf{Design and implementation of photo-responsive self-deforming structures 
    (Sponsor: NRF (Korea))}
    \begin{itemize}
        \item Developed finite element method that considers \textbf{a multiphysics} of photo-responsive polymer using \textbf{nonlinear, shell element}
        \item Proposed a \textit{multiscale} method to address light-driven structural behavior
        \item Presented nonlinear thermoelastic instability of nematic polymer with disclination defects
        \item Lead a task force team to design a polymer synthesis lab in SNU
    \end{itemize}
    
    % \item \textbf{Development of web-based multiscale simulation platform for an efficient design of energy nanomaterials (Sponsor: Ministry of Knowledge Economy (Korea))}
    \item \textbf{Development of nano-continuum bridging technology for microscopic structure design (Sponsor: NRF (Korea))}
    \begin{itemize}
        \item Studied static sub-micro structural behaviors of bicrystal using molecular dynamics simulation
        \item Developed a multi-scale analysis model for nanostructures using a molecular dynamics coupled with continuum mechanics 
        
    \end{itemize}
    
    % \item \textbf{Multi-scale approach for nanocarbon-based composites’ electro/thermo-conductive behaviors (Collaboration: KIST (Korea))}
\end{enumerate}

%----------------------------------------------------------------------------------------
%	TECHNICAL SKILLS SECTION
%----------------------------------------------------------------------------------------

\section{TECHNICAL \\ SKILLS} 

\textbf{Programming Languages:} Matlab, C++, Python, Mathematica. \\
\textbf{Programming Libraries:} Numpy, Scipy, Eigen, LAPACK, NLOPT, HSL, Boost, Cython \\
\textbf{ Structural Analysis:} In-house programming, ABAQUS \\
\textbf{ Optimization:} OpenMDAO (MDO), Optistruct (Toplogy optimization) \\
\textbf{ Molecular Dynamics:} LAMMPS, Materials Studio \\
\textbf{ Operating System:} Windows, Linux \\
\textbf{ MISC.:} LaTex, MS offices \\
 

%----------------------------------------------------------------------------------------
%	PUBLICATION
%----------------------------------------------------------------------------------------
 
\section{PUBLICATION \\ IN JOURNALS}

\begin{enumerate}
    \item \textbf{Hayoung Chung}, Oded Amir, Alicia H. Kim, “Level-set topology optimization considering nonlinear thermoelasticity”, \textit{Submitted}. % 
    \item Gang-Won Jang, Sandilya Kambampati, \textbf{Hayoung Chung}, Alicia H. Kim, “Configuration Optimization for Uniform Thickness Structures Using Level Set Method”, \textit{Submitted}.
    \item \textbf{Hayoung Chung}, John T. Hwang, Justin Gray, Alicia H. Kim, “Topology Optimization in OpenMDAO”, \textit{Submitted}.
    \item Jaesung Park, \textbf{Hayoung Chung}, Maenghyo Cho, “Strain pattern search simulation of liquid-crystalline self-deforming device according to topology optimization and using the nonlinear FEM”, \textit{In preparation}. 
    %% belows are published works
    \item \textbf{Hayoung Chung}, Maenghyo Cho, “Biased propagation of intergranular fracture: a molecular dynamics study”, Journal of Mechanical Science and Technology (32), 11, 5351-5361, 2018. 11 % 2018 11 07
    \item Jung-Hoon Yun, Chenzhe Li, \textbf{Hayoung Chung}, Joonmyung Choi, Maenghyo Cho, ” Multiscale modeling and its validation of the trans-cis-trans reorientation-based photodeformation in azobenzene-doped liquid crystal polymer”, International Journal of Solids and Structures, Accepted, 2017. 08 % 2017 12 01
    \item \textbf{Hayoung Chung}, Jaesung park, Maenghyo Cho, “Numerical study of light-induced phase behavior of smectic solids”, Physical Review E (94), 42707, American Physical Society, 2016.10.  % 2016 10 26
    \item Hayoung Chung, \textbf{Jung-Hoon Yun}, Joonmyung Choi, Maenghyo Cho, "Finite-element analysis of the optical-texture-mediated photoresponse in a nematic strip", Computational Mechanics (14), 1-14, 2016.10. % 2016 10 14
    \item Joonmyung Choi, \textbf{Hayoung Chung}, Jung-Hoon Yun, Maenghyo Cho (2016) “Molecular Dynamics Study on the Photothermal Actuation of a Glassy Photoresponsive Polymer Reinforced with Gold Nanoparticles with Size Effect”. ACS Applied Materials \& Interfaces (8):24008–24024.  % 2016 09 23
    \item \textbf{Hayoung Chung}, Joonmyung Choi, Jung-Hoon Yun, Maenghyo Cho, "Nonlinear photomechanics of nematic networks: upscaling microscopic behaviour to macroscopic deformation", Scientific Reports (6), 20026 2016.02. % 2016 02 01
    \item Seongseop Kim, Wonbae Kim, \textbf{Hayoung Chung}, and Maenghyo Cho, "Asymmetric surface effect on the configuration of bilayer Si/SiGe nanosprings ", RSC Advances (5), 96387, 2015.11,  %2015 11 10
    \item Jung-Hoon Yun, Chenzhe Li, \textbf{Hayoung Chung}, Joonmyung Choi, Maenghyo Cho, "Photo Deformation in Azobenzene Liquid-crystal Network: Multiscale Model Prediction and Its Validation", Polymer (75), 51-56, Elsevier Science Ltd., 2015.09. % 2015 09 28
    \item Wonbae Kim,\textbf{Hayoung Chung}, Maenghyo Cho, "Anisotropic Hyperelastic Modeling for Face-Centered Cubic and Diamond Cubic Structures", Computer Methods in Applied Mechanics and Engineering, Elsevier (291), 216-239, Elsevier, 2015.07. % 2015 07 01
    \item Jung-Hoon Yun, Chenzhe Li, \textbf{Hayoung Chung}, Joonmyung Choi, Maenghyo Cho, "Predicting Photoisomerization Profile of the Highly Polymerized Nematic Azobenzene Liquid Crystal Network: First Principle Calculation.", Chemical Physics Letters (627), 20, Elsevier, 2015.03. %2015 03 18
    \item \textbf{Hayoung Chung}, Joonmyung Choi, Jung-Hoon Yun, Maenghyo Cho., "Light and thermal responses of liquid crystal network films: A finite element study", Physical Review E, also selected as a part of Kaleidoscope (91), 042503, American Physical Society, 2015.03. % 2015 04 10
    \item Joonmyung Choi, \textbf{Hayoung Chung}, Jung-Hoon Yun, Maenghyo Cho, "Photo-isomerization effect of the azobenzene chain on the opto-mechanical behavior of nematic polymer: A molecular dynamics study", Applied Physics Letters (105), 22, 221906, American Institute of Physics, 2014.12.  % 2014 12 02
    \item Wonbae Kim, \textbf{Hayoung Chung}, Maenghyo Cho, "Length and boundary effects on a nanorod", AIP Advances (2), 042166, American Institute of Physics, 2012.11.
    
\end{enumerate}

\section{International \\ Conferences}

\begin{enumerate}
    % M2DO
    \item \textbf{Hayoung Chung}, Oded Amir, Hyunsun A. Kim "Nonlinear Thermoelastic Topology Optimization with the Level-Set Method", AIAA SciTech Conference, 2019.01. San Diego, CA, USA.
    \item Sandilya Kambampati, Zongliang Du, \textbf{Hayoung Chung}, Hyunsun A. Kim, Carolina Jauregui, Scott Townsend, Renato Picelli, Xiao-Yi Zhou, and Lester Hedges, "OpenLSTO: Open-Source Software for Level Set Topology Optimization", Multidisciplinary Analysis and Optimization Conference, 2018.06. Atlanta, USA.
    \item \textbf{Hayoung Chung}, John T. Hwang, Justin S. Gray, Hyunsun A. Kim, "Implementation of topology optimization using openMDAO," AIAA SciTech Conference, 2018.01, Kissimmee, FL, USA.
    \item Zongliang Du, \textbf{Hayoung Chung}, Sandilya Kambampati, Hyunsun A. Kim, "Multiscale design with architected material connectivity for multiphysics problems", TMS 2018, 2018.03, Arizona, USA.
    
        % SSND
    \item Joonmyung Choi, \textbf{Hayoung Chung}, Hyunseong Shin, Jung-Hoon Yun, Maenghyo Cho, " Computational multiscale modeling of light-responsive polymer nanocomposites and the associated interphases ", The 10th Asian-Australasian Conference on Composite Materials (ACCM-10), 2016.10, Busan, Korea.
    \item Joonmyung Choi, Hyunseong Shin, \textbf{Hayoung Chung}, Maenghyo Cho, " An all-atom simulation and its multiscale mechanical model for the photo-responsive polymer reinforced with gold nanoparticles ", 26th International Liquid Crystal Conference (ILCC 2016), 2016.08, Kent, OH, USA.
    \item Jaesung Park, \textbf{Hayoung Chung}, Maenghyo Cho, " Design of photo-responsive actuation; Light and texture modulation ", 26th International Liquid Crystal Conference (ILCC 2016), 2016.08, Kent, OH, USA.
    \item Jung-Hoon Yun, Chenzhe Li, \textbf{Hayoung Chung}, Joonmyung Choi, Maenghyo Cho, " Predicting Photo Deformation of the Azobenzene Doped Liquid-crystalline Polymer ", 26th International Liquid Crystal Conference (ILCC 2016), 2016.08, Kent, OH, USA.
    \item Joonmyung Choi, \textbf{Hayoung Chung}, Hyunseong Shin, Maenghyo Cho, " A multiscale design approach for the optically actuated polymer nanocomposites and the associated interphases ", 12th World Congress on Computational Mechanics \& 6th Asian Pacific Congress on Computational Mechanics (WCCM XII \& APCOM VI), 2016.07, Seoul, Korea.
    \item \textbf{Hayoung Chung}, Joonmyung Choi, Maenghyo Cho, " Bridging micro-macro behavior of photo-responsive polymer: revealing nonlinear photomechanics ", 12th World Congress on Computational Mechanics \& 6th Asian Pacific Congress on Computational Mechanics (WCCM XII \& APCOM VI), 2016.07, Seoul, Korea.
    \item Jaesung Park, \textbf{Hayoung Chung}, Maenghyo Cho, " Multiscale based design framework of irradiation pattern on the photo-responsive polymer; a topology optimization ", 12th World Congress on Computational Mechanics \& 6th Asian Pacific Congress on Computational Mechanics (WCCM XII \& APCOM VI), 2016.07, Seoul, Korea.
    \item Joonmyung Choi, Junghwan Moon, \textbf{Hayoung Chung}, Maenghyo Cho, " A method of molecular computation of photo-responsive polymer reinforced with nanoparticles ", 3rd International Conference on Computational Design in Engineering (CODE2015), 2015.12, Tokyo, Japan.
    \item \textbf{Hayoung Chung}, Jaesung Park, Joonmyung Choi, Jung-Hoon Yun, Maenghyo Cho, " A finite element study about mechancial frustration of nematic solids induced by disclination defect ", 3rd International Conference on Computational Design in Engineering (CODE2015), 2015.12, Tokyo, Japan.
    \item Joonmyung Choi, \textbf{Hayoung Chung}, Jung-Hoon Yun, Maenghyo Cho, " Molecular dynamics simulation model for the photo-responsive polymer and its nanocomposites ", The 2015 world congress on advances in structural engineering and mechanics (ASEM15), 2015.08, Incheon, Korea.
    \item Jung-Hoon Yun, Chenzhe Li, \textbf{Hayoung Chung}, Joonmyung Choi, Maenghyo Cho, " Modeling Photoisomerization of Azobenzene and Its Validation ", The 2015 World Congress on Advances in Structural Engineering and Mechanics (ASEM15), 2015.08, Incheon, Korea.
    \item \textbf{Hayoung Chung}, Joonmyung Choi, Jung-Hoon Yun, Jaesung Park, Maenghyo Cho, " Multiscale design framework of photo-responsive mechanism ", Asian Conference on Liquid Crystals (ACLC2015), The Korea Liquid Crystal society, (Best Poster Award), 2015.01, Busan, South Korea.
    \item Jung-Hoon Yun, \textbf{Hayoung Chung}, Joonmyung Choi, Chenzhe Li, Junghwan Moon, Maenghyo Cho, " Light Penetration Modeling in Azobenzene Liquid Crystal Elastomer ", Asian Conference on Liquid Crystals (ACLC2015), The Korean Liquid Crystal Society, 2015.01, Busan, South Korea.
    \item Jaesung Park, \textbf{Hayoung Chung}, Maenghyo Cho, " Design of Application-oriented Photo Responsive Polymer Devices based on Optimization Technique ", 5th International Conference on Computational Methods (ICCM2014), 2014.07, Cambridge, United Kingdom.
    \item \textbf{Hayoung Chung}, Jung-Hoon Yun, Joonmyung Choi, Maenghyo Cho, " An investigation on disclination defect and nematic order coupled nonlinear behavior of liquid crystal glassy polymer using quasi-soft energy ", 5th International Conference on Computational Methods (ICCM2014), 2014.07, Cambridge, United Kingdom.
    \item Jung-Hoon Yun, \textbf{Hayoung Chung}, Joonmyung Choi, Maenghyo Cho, " Photoisomerization and light penetration modelling in Liquid Crystal Elastomer ", 25th International Liquid Crystal Conference, 2014.07, Dublin, Ireland.
    \item Joonmyung Choi, \textbf{Hayoung Chung}, Jung-Hoon Yun, Maenghyo Cho, " Opto-mechanical behavior of Azobenzene-doped liquid crystalline polymer: A molecular dynamics study ", 5th International Conference on Computational Methods (ICCM2014), 2014.07, Cambridge, United Kingdom.
    \item Jung-Hoon Yun, \textbf{Hayoung Chung}, Joonmyung Choi, Maenghyo Cho, " Photoisomerization and light penetration modelling in liquid crystal elastomer ", 25th International Liquid Crystal Conference, 2014.07, Dublin, Ireland.
    \item Maenghyo Cho, Jung-Hoon Yun, Joonmyung Choi, \textbf{Hayoung Chung}, " A multiscale/multiphysics platform for analysis and design of photo-responsive polymer ", 5th International Conference on Computational Methods (ICCM2014), 2014.07, Cambridge, United Kingdom.
    \item \textbf{Hayoung Chung}, Joonmyung Choi, Jung-Hoon Yun, Maenghyo Cho, " Design of photoresponsive polymer based on multiscale analysis ", 5th Asia Pacific Congress on Computational Mechanics (APCOM2013) and 4th international Symposium on Computational Mechanics (ISCM2013), 2013.12, Singapore.
    \item \textbf{Hayoung Chung}, Maenghyo Cho, " Study on directional preference of crack propagation ", International Conference on Advances in Interaction \& Multiscale Mechanics (AIMM'13), 2013.09, Jeju, Korea.
    \item \textbf{Hayoung Chung}, Maenghyo Cho, " A study on the fracture of bicrystal by molecular dynamics simulation ", 2nd International Conference on Computational Design in Engineering (CODE 2012), Computational Structural Engineering Institute of Korea, 2012.11, Jeju, Korea.
    \item \textbf{Hayoung Chung}, Maeghyo Cho, " A FINITE ELEMENT ANALYSIS ON FRACTURE OF POLYCRYSTALLINE STRUCTURE USING COHESIVE ZONE MODEL (CZM) APPROACH ", 10th world congress of computational mechanics(WCCM 2012), 2012.07, Sao Paulo, Brazil.
    \item Seongseop Kim, Wonbae Kim, \textbf{Hayoung Chung}, Maenghyo Cho, " Effect of width to thickness ratio and tilt angle on the Si/SiGe bilayer nanospring ", International Conference on Advances in Interaction \& Multiscale Mechanics (AIMM'11), 2011.09, Seoul, Korea.
    \item \textbf{Hayoung Chung}, Wonbae Kim, Maenghyo Cho, " Surface relaxation model for zinc blende structure ", International Conference on Advances in Interaction \& Multiscale Mechanics (AIMM'11), 2011.09, Seoul, Korea.
    \item Seongseop Kim, Wonbae Kim, \textbf{Hayoung Chung}, Maenghyo Cho, " Multiscale Analysis of Equilibrium Configuration of Nanospring Considering Surface Effect ", 11th U.S. National Congress on Computational Mechanics, USACM, 2011.07, Minneapolis, USA.
    \item \textbf{Hayoung Chung}, Wonbae Kim, Maenghyo Cho, " A Surface Relaxation Model of Si (001) Thin Film for Calculation of Thickness Dependent Properties ", 11th U.S. National Congress on Computational Mechanics, USACM, 2011.07, Minneapolis, USA..
\end{enumerate}

%----------------------------------------------------------------------------------------
%	Teaching experiences
%----------------------------------------------------------------------------------------
\section{TEACHING \\EXPERIENCES}
\begin{enumerate}
    \item \textbf{Topology optimization for additive manufacturing} \hfill 2018, Fall (UCSD) \\
    Guest lecture \\
    Mentoring student projects \\

    \item \textbf{Optimization} \hfill 2018, Fall (UCSD) \\
    Guest lecture \\

    \item \textbf{Osptimization} \hfill 2017, Fall (UCSD) \\
    Guest lecture \\
    
    \item \textbf{Numerical analysis on plate and shells} \hfill 2015, Fall (SNU) \\
    Preparing lecture materials \\
    Complementary lectures \\
    
    \item \textbf{Multiscale simulations } \hfill 2013, Spring (SNU)\\
    Preparing lecture materials \\
	MD simulation demonstration\\
	Nonlinear finite element analysis programming demonstration\\

    \item \textbf{Multiscale simulations } \hfill 2012, Fall (SNU)\\
    Preparing lecture materials \\
	MD simulation demonstration \\
    
    \item \textbf{Continuum Mechanics } \hfill 2011, Fall (SNU)\\
	Preparing lecture materials \\
	Tutorial for Total/Update Lagrangian formulation 

\end{enumerate}

%----------------------------------------------------------------------------------------
%	Service to Profession
%----------------------------------------------------------------------------------------
\section{SERVICE TO \\ PROFESSION}

\textbf{Peer review: }
Structural and Multidisciplinary Optimization (4 papers) \\
\textbf{Session chair: }
MDO-11, AIAA Science and Technology Forum and Exposition, 2018
%----------------------------------------------------------------------------------------
%	Awards and Honors
%----------------------------------------------------------------------------------------
\section{AWARDS AND \\ HONORS}
\begin{itemize}
    \item \textbf{Kaleidoscope}, \textit{Physical Review E}, 2015
    \item \textbf{Best poster award}, Symposium on the Multiscale \& Multiphysics Mechanics (MMM), awarded by the chair of Korean Society of Mechanical Engineers (KSME), Dec. 2014 
    \item \textbf{Best poster award}, Asian Conference on Liquid Crystals (ACLC 2015), Jan. 2015
\end{itemize}
%----------------------------------------------------------------------------------------
%	Lists of References
%----------------------------------------------------------------------------------------
% \section{REFERENCE LIST}
% \begin{enumerate}
%     \item \textbf{Prof. Maenghyo Cho} \\
%     Multiscale Division, Department of Mechanical Engineering, \\
%     Seoul National University \\
%     mhcho@snu.ac.kr \\
    
%     \item \textbf{Prof. Hyun-Gyu Kim}\\
%     Department of Mechanical Engineering\\
%     Seoul National University of Science \& Technology\\
%     khg@seoultech.ac.kr \\ 
    
%     \item \textbf{Prof. Do-Nyun Kim}\\
%     Department of Mechanical and Aerospace Engineering, \\
%     Seoul National University\\
%     dnkim@snu.ac.kr\\
    
%     \item \textbf{Prof. Alicia Kim}\\
%     Structural Engineering,  \\
%     University of California, San Diego\\
%     hak113@eng.ucsd.edu \\
    
%     \item \textbf{Prof. John T. Hwang}\\
%     Mechanical and Aerospace Engineering  \\
%     University of California, San Diego\\
%     jhwang@eng.ucsd.edu \\
    
%     \item \textbf{Dr. Justin S. Gray}\\
%     NASA Glenn Research Center  \\
%     justin.s.gray@nasa.gov \\
% \end{enumerate}

\end{resume}
\end{document}